### 2021-03-11 ch/2-related-work.tex
Extend literature review

This topic has since received more contributions than I can explain here,
so I will just point to them.
In the direction of \citet{zafar2017fairnessconstraints}, there is \citet{quadrianto2017recycling}.
In the direction of \citet{kamiran2012data}, there is \citet{AgaBeyDudLanetal18,roh2021fairbatch}.

@@

>>>>

This topic has since received more contributions than I can explain here,
so I will just point to them.
In the direction of \citet{zafar2017fairnessconstraints}, there is \citet{quadrianto2017recycling,lohaus2020too}.
In the direction of \citet{kamiran2012data}, there is \citet{AgaBeyDudLanetal18,roh2021fairbatch}.

@@

A perceived shortcoming of most methods in this area is that they rely on annotations for the subgroups.
Two papers that tried to circumvent this problem are \citet{HasSriNamLia18,nam2020learning},
both taking very different routes.
The first one tries to be robust with respect to all possible subgroups down to a certain size.
Essentially, the method tackles the worst-case scenario where the most egregiously misclassified samples form a subgroup.
The second approach is based on the idea that subgroups are easier to predict than the actual prediction targets.
After all, if this were not the case, then there would not really be a problem.
Thus, a classifier is learned in such a way that it predominantly tries to make ``easy'' predictions,
that is, samples where the model is very confident receive a higher weight.
The assumption is that this model learns to predict the subgroup (or spurious attribute),
for which no labels are available.
A second model is then trained, for which those samples are downweighted for which the first model was very confident;
the hope being that by learning the ``hard'' samples, the model learns the correct relationship.
Both \citet{HasSriNamLia18,nam2020learning} frame their methods as improving accuracy on an unbiased test set
and do not make references to fairness metrics,
but there is nevertheless a strong connection to the fairness literature.

### 2021-03-11 ch/4-structure.tex
Extend literature review

\chapter{Summary of contributions}\label{ch:content}
The main contributions of this thesis are as follows.
All presented approaches rely on some form of side information with allows us to overcome the dataset bias.
This side information is always significantly easier to obtain than unbiased data.

\section{Using target labels to mitigate label bias}\label{sec:target-labels}
\citet{kehrenberg2020tuning} (\chapref{ch:paper1}) is predominantly concerned with label bias.
The main idea is that we make use of pseudo labels (or \emph{target labels})
to implicitly learn from a \emph{balanced} dataset,
in which \(y\perp s\) holds, and which thus satisfies \acf{DP}.
This falls under the area of \emph{fair classifiers} discussed in \secref{fair-classifiers}

>>>>

\chapter{Summary of contributions}\label{ch:content}
The following is a summary of the main contributions in this thesis.
All presented approaches deal with dataset bias that is closely linked to a special attribute $s$.
Furthermore, the approaches all rely on some form of side information with allows us to overcome dataset bias.
This side information is always significantly easier to obtain than unbiased data.

\section{Using target labels to mitigate label bias}\label{sec:target-labels}
\citet{kehrenberg2020tuning} (\chapref{ch:paper1}) is predominantly concerned with label bias.
More precisely, labels \(y\) are flipped with a probability and a direction that depends on a sensitive attribute \(s\).
The main idea is that we make use of pseudo labels (or \emph{target labels})
to implicitly learn from a \emph{balanced} dataset,
in which \(y\perp s\) holds, and which thus satisfies \acf{DP}.
This falls under the area of \emph{fair classifiers} discussed in \secref{fair-classifiers}
